An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2022-03-10 gas-adsorption/gas-ads-prresearch.tex
add upload to arxiv
start working on referee response

\documentclass[pre,twocolumn]{revtex4-2}

@@

@@

A promising approach to densify natural
gas~\cite{makal2012methane,mason2014evaluating} and
hydrogen~\cite{suh2011hydrogen,garcia2018benchmark} for vehicular storage at
room temperature is through physical adsorption in nanoporous
materials~\cite{schoedel2016role}. The internal surfaces of porous materials
attract gas molecules through van der Waals, electrostatic, etc.\ interactions
to achieve a higher adsorbed gas density than the bulk gas at the same
temperature and pressure.
Nanoporous materials could thus allow for room temperature and lower-pressure
storage of natural gas and hydrogen and alleviate many drawbacks of high-pressure or low-temperature
storage.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{hydrogen-298-n-vs-G}
    \caption{Deliverable capacity of hydrogen at room temperature as a function of the attractive Gibbs free energy $|\gst|$.  Experimental deliverable capacities for several porous materials (data from Ref.~\cite{garcia2018benchmark}) are shown along with the experimental values for $\gst$ at the empty and full pressures shown as $+$'s connected by a line.}
    \label{fig:hydrogen-298-D}
\end{figure}

>>>>

\documentclass[aps,prl,twocolumn]{revtex4-2}

@@

\title{An upper bound to gas storage and delivery via pressure-swing adsorption in
porous materials}

@@

A promising approach to densify natural
gas~\cite{makal2012methane,mason2014evaluating} and
hydrogen~\cite{suh2011hydrogen,garcia2018benchmark, record-high-hydrogen-storage-2018} for vehicular storage at
room temperature is through physical adsorption in nanoporous
materials~\cite{schoedel2016role}. The internal surfaces of porous materials
attract gas molecules through van der Waals, electrostatic, etc.\ interactions
to achieve a higher adsorbed gas density than the bulk gas at the same
temperature and pressure.
Nanoporous materials could thus allow for room temperature and lower-pressure
storage of natural gas and hydrogen and alleviate many drawbacks of high-pressure or low-temperature
storage.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{hydrogen-298-n-vs-G}
    \caption{Deliverable capacity of hydrogen at room temperature as a function
    of the attractive Gibbs free energy $|\gst|$.  Experimental deliverable
    capacities for several porous materials (data from
    Ref.~\cite{garcia2018benchmark, record-high-hydrogen-storage-2018}) are shown along with the experimental
    values for $\gst$ at the empty and full pressures shown as $+$'s connected
    by a line.}
    \label{fig:hydrogen-298-D}
\end{figure}
